 

### 2020-12-04 doc/manuscript/tables_figures/tables.Rmd
fix up species table, format in tables.Rmd
#36

#add footnote: 
kableExtra::footnote(number = c("One of nine species analyzed had significant positive response to April $T_{max}$; two had significant negative response to March $T_{max}$", "One of two species analyzed had signficant positive response to April $T_{max}$, both had negative response to May $T_{max}$", "The one species analyzed had a signficant negative response to April $T_{max}$."), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```

>>>>

#add footnote: 
kableExtra::footnote(number = c("One of nine species analyzed had significant positive response to April $T_{max}$; one had significant negative response to March $T_{max}$", "One of two species analyzed had signficant positive response to April $T_{max}$, both had negative response to May $T_{max}$", "The one species analyzed had a signficant negative response to April $T_{max}$."), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```

\newpage
```{r species_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
species_table <- read.csv(file = "species_table.csv", col.names = c("site", "xylem porosity","species","n trees", "n tree-years", "n cores", "date range"),  stringsAsFactors = FALSE, check.names = FALSE)
kable(species_table, caption = "Table 2. Dominant ring- and diffuse-porous species at SCBI and Harvard Forest analyzed here, along with sample sizes.",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ", " ", " ", "Dendrometer Bands" = 2, "Tree Cores"=2 )) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
